### 2014-06-26 0_frontmatter/abstract.tex
auto

%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page

@@

As a result of these studies, several scalar statistical models based on the determinant of POLSAR covariance matrix are proposed and validated.
These generic models for POLSAR are also shown to be both multiplicative and heteroskedastic, similar to the models for SAR intensity. 
Subsequently, logarithmic transformation is applied onto both SAR and POLSAR models
  to convert them into additive and homoskedastic models.
From these models, the benefits of homoskedastic statistical estimation framework are then further explored.

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,
  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For example, for inexperienced researchers (such as this author when he began this research),
  this thesis proposes additive and homoskedastic models for both SAR and POLSAR data,
  which are simpler and more familiar.
They are helpful by keeping these inexperienced researchers from falling into several common traps in (POL)SAR data processing.
%For inexperienced researchers (such as this author when he began this research),
%  who attempt to process either SAR or POLSAR data using existing computation algorithms
%  which most of the time expect an additive and homoskedastic input,
%  this thesis proposes alternative and more familiar additive and homoskedastic models.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the statistical estimation framework for (POL)SAR.

>>>>

%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page
\phantomsection
\addcontentsline{toc}{section}{Abstract Summary}

@@

As a result of these studies, several scalar statistical models based on the determinant of POLSAR covariance matrix, namely the determinant and the determinant-ratio models, are proposed and validated.
These generic models for POLSAR are also shown to be both multiplicative and heteroskedastic, similar to the models for SAR intensity. 
Subsequently, logarithmic transformation is applied onto both SAR and POLSAR models
  to convert them into additive and homoskedastic models.
These models includes: the log-determinant, the log-distance, the dispersion and the contrast models.
%From these models, the benefits of homoskedastic statistical estimation framework are then further explored.

Since the full POLSAR data is multi-dimensional and the proposed models are scalar, they are not perfect.
Specifically, they suffers from a loss of dimension.
Still there are several beneficial implications of the models proposed in this thesis. 
Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,
  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For example, for inexperienced researchers (such as this author when he began this research),
  this thesis proposes additive and homoskedastic models for both SAR and POLSAR data,
  which are simpler and more familiar.
They are helpful by keeping these inexperienced researchers from falling into several common traps in (POL)SAR data processing.
%For inexperienced researchers (such as this author when he began this research),
%  who attempt to process either SAR or POLSAR data using existing computation algorithms
%  which most of the time expect an additive and homoskedastic input,
%  this thesis proposes alternative and more familiar additive and homoskedastic models.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the statistical estimation framework for (POL)SAR.

### 2014-06-26 1_introduction/introduction.tex
auto

%Given the BIG problem, Why it is important to solve this problem?
The
                big picture, as introduced above, is that POLSAR data is multi-dimensional,
                stochastic, multiplicative and heteroskedastic.
%Under
%                this context, the motivation is to gain a better
%                understanding of the data,
%which
%                hopefully will lead to better information that can be
%                extracted from these data.
Under this condition, it is very important to understand the statistical models for its
data. It is these models that form the foundation for different (POL)SAR data processing
techniques, for example speckle filtering, target detection, image segmentation, and
other clustering, classification techniques.
In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
which comprises statistical modelling and validation, estimator design and development
as well as evaluation of different estimators' accuracy. And central to this statistical
estimation theory is the need for statistically consistent discrimination measures which
are commonly derived from the statistical models.

@@

%Solving these dual-problem is both important and interesting.
%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data. % dear Ian I changed this back 
%of the Additive White Gaussian Noise (AWGN) model in natural processes.
%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive. However this is definitely not true - your POLSAR data is digital and yet is not additive. Maybe you can say "or the prevalence of AWGN in the majority of sensing or sampling systems, and electronic devices."
%OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
%****IVM2: I'm still not sure about it, but we can put it to the examiner, see if he picks it up.
It should be noted that even for the case of SAR data which is digital and not additive,
  the above statement is still true as SAR actually has two components, the real and imaginary parts,
  both of which follow the standard Additive White Gaussian Noise model.
%****IVM: I really don't understand what you're trying to say here.  Are you saying that "both parts are corrupted by AWGN"?

Both SAR and POLSAR data however are multiplicative and heteroskedastic by nature.
While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility. 
An example is the use of mean, variance and squared error criteria, which are linear by nature and work excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
Such use, however, is known to be not very robust for these so-called heavy tailed distributions.

Similarly, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criterion which is probably due to the Gauss Markov theorem.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.

@@

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  submitted to \textit{IET Radar, Sonar \& Navigation}
\end{enumerate}

>>>>

%Given the BIG problem, Why it is important to solve this problem?
The
                big picture, as introduced above, is that POLSAR data is multi-dimensional,
                stochastic, multiplicative and heteroskedastic.
%Under
%                this context, the motivation is to gain a better
%                understanding of the data,
%which
%                hopefully will lead to better information that can be
%                extracted from these data.
Under this condition, it is very important to understand the statistical models for its
data. It is these models that form the foundation for different (POL)SAR data processing
techniques, for example speckle filtering, target detection, image segmentation, and
other clustering, classification techniques \cite{Lopez-Martinez_2003_TGRS_2232, Argenti_GRSM_2013, Conradsen_2003_TGRS_4}.
In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
which comprises statistical modelling and validation, estimator design and development
as well as evaluation of different estimators' accuracy. And central to this statistical
estimation theory is the need for statistically consistent discrimination measures which
are commonly derived from the statistical models.

@@

%Solving these dual-problem is both important and interesting.
%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.
In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data. % dear Ian I changed this back 
%of the Additive White Gaussian Noise (AWGN) model in natural processes.
%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive. However this is definitely not true - your POLSAR data is digital and yet is not additive. Maybe you can say "or the prevalence of AWGN in the majority of sensing or sampling systems, and electronic devices."
%OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
%****IVM2: I'm still not sure about it, but we can put it to the examiner, see if he picks it up.
It should be noted that even for the case of SAR data which is digital and not additive,
  the above statement is still true as SAR actually has two components, the real and imaginary parts,
  both of which follow the standard Additive White Gaussian Noise model.
%****IVM: I really don't understand what you're trying to say here.  Are you saying that "both parts are corrupted by AWGN"?

Both SAR and POLSAR data however are multiplicative and heteroskedastic by nature.
While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility. 
An example is the use of mean, variance and squared error criteria, which are linear by nature and work excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
Such use, however, is known to be not very robust for these so-called heavy tailed distributions \cite{McElroy_Econometric_2002}.

Similarly, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure \cite{Rignot_1993_TGRS_896}.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criterion which is probably due to the Gauss Markov theorem \cite{Furno_1991_JStatCompSimul}.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed \cite{Gagnon_SPIEProc_1997, Argenti_GRSM_2013}.

@@

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  under revision for resubmission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  submitted to \textit{IET Radar, Sonar \& Navigation}
\end{enumerate}
